\centering Syscoin 4.0: A Peer-to-Peer Electronic Cash System Built For Business Applications

### 2021-01-26 syscoin_4.0/article.tex
lorem lpsum

\begin{abstract}
Syscoin 4.0 introduces a novel implementation of a decentralized identity, zero-knowledge proofs, masternodes providing bonded validators for a PoW/PoS hybrid consensus model (Nakamoto DAG) and instant pseudo-interactive zero-confirmation cryptocurrency transactions with double-spend protection.
\end{abstract}

>>>>

\begin{abstract}
Syscoin 4.0 introduces a novel implementation of a decentralized identityz masternodes providing bonded validators for a PoW/PoS hybrid consensus model (Nakamoto DAG) / zero knowledge proofs and instant pseudo-interactive zero-confirmation cryptocurrency transactions with double-spend protection.
\end{abstract}
